---
title: "Résumé"
author: "Wendy Phillips"
date: "8/12/2023"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    dev: cairo_pdf
    template: svm-latex-resume.tex
fontawesome: FALSE
linestretch: TRUE
colorlinks: TRUE

geometry: "top=.75in, left =.75in, right=.75in, bottom=.75in"
mainfont: Proxima Nova
sansfont: Proxima Nova
monofont: Proxima Nova 
urlcolor: CadetBlue
fontsize: 11pt
summary: "Propelled by curiosity to uncover hidden gems in data, with out-of-the-box thinking that solves problems. My insight into others' needs drives my clear, impactful communication of results."  

includephoto: FALSE
---

```{r setup, include=FALSE, echo=FALSE}
library(tidyverse)
library(RColorBrewer)
```

:::::: {.columns}
::: {.column width="57%" data-latex="{0.57\textwidth}"}

# EXPERIENCE
\vspace{0em}
## **WORK ACTIVITY HISTORY**
```{r, echo=FALSE, message = FALSE}
# Read in and subset data
act <- read.csv("data/Activities.csv", check.names = FALSE)
act <- act[, 1:9]

# Transform to long format for plotting
act_long <- act |> pivot_longer(cols = 2:9)
act_long <- act_long |> rename(Activity = name)

# Change underscore to space
act_long$Activity <- gsub("Analyze_data", "Analyze data", act_long$Activity)

# Factor activities by desired plotting order
act_long$Activity <- factor(act_long$Activity, level = c("Analyze data", "Research", "Write", "Present", "Learn", "Teach", "Create", "Other"))

# pal <- c(brewer.pal(6,"Dark2"), "#573db3")
wp_cols <- c( "#0054bd", "#ff9b62", "#524685", "#ffc680", "#3b907b","#019af1","#755ad6", "#89909e", "#85c25b","#cb002f")
#wp_cols <- c("#3a6ce3", "#6dd5db", "#783fcf", "#e399ff", "#005995", "#bec3dc", "#3b907b", "#89909e", "#e08f71")
ggplot(act_long, aes(x = Year, y = value, fill = Activity)) +
  geom_area(stat = "identity", position = "stack") +
  theme_classic(base_size = 14) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0), breaks = c(2000, 2005, 2010, 2015, 2020)) +
  labs(y = "Percent of working time") +
  theme(legend.position = "top") +
  scale_fill_manual(values = wp_cols)
  # scale_fill_brewer(type = "qual", palette = "Dark2")
```


## \textcolor{BlueViolet}{Senior Bioinformatician}
\vspace{-0.75em}
2020 - present, *Diversigen*, New Brighton, MN  

\small
\vspace{-0.65em}
- Engage with internal and external teams to understand project goals, execute analyses, return figures and statistical results, producing and presenting over 20 reports
- Create R package of visualization and statistical functions used by team members, incorporate feedback, maintain on GitHub
- Spearhead analysis of multi-faceted internal research project, present findings at national conference
- Collaborate with team to perform and receive reviews of code and reports, address and incorporate feedback

\vspace{-1.5em}
## \textcolor{BlueViolet}{Research Scientist}
\vspace{-0.75em}
2018 - 2020, *Elanco*, Greenfield, IN 

\vspace{-0.65em}
- Performed quality control, exploratory & statistical analysis on research data, produced summary visualizations, wrote reports
- Presented findings to internal teams and at external conferences, customizing information for audience backgrounds
- Taught team members basic analytic and visualization methods

\vspace{-1.5em}
## \textcolor{BlueViolet}{Business Owner}
\vspace{-0.75em}
2016 - 2018, *Wendy Phillips Photography*, Corvallis, OR

\vspace{-0.65em}
- Founded and managed self-owned photography business

\vspace{-1.5em}
## \textcolor{BlueViolet}{Research Associate}
\vspace{-0.75em}
2013 - 2016, *U.S. Dept. of Agriculture*,  Corvallis, OR  

\vspace{-0.65em}
- Managed five concurrent research projects, performed research and data analyses, yielding five scientific publications

:::
::: {.column width="5%" data-latex="{0.05\textwidth}"}
\ 
<!-- an empty div with an empty character to serve as a column sep -->
:::
:::::: {.column width="38%" data-latex="{0.38\textwidth}"}

# CONTACT INFORMATION
\vspace{-0.5em}
wendyphillips@gmail.com  
541-230-8048  
Golden Valley, MN  

\vspace{-0.75em}
# LINKS
\vspace{-0.5em}
[GitHub](https://github.com/wendysphillips)  
[LinkedIn](https://https://www.linkedin.com/in/wendyphillipsphd/)  

\vspace{-0.75em}
# EDUCATION
\vspace{-0.5em}
**Ph.D.** Environmental Sciences  
Oregon State University, 2012   

**B.A.** Biological Sciences  
The University of Chicago, 1992 

\vspace{-0.75em}
# CERTIFICATIONS
\vspace{-0.5em}
[Professional Data Scientist](https://www.datacamp.com/certificate/DS0027755206453)      
DataCamp, 2023

\vspace{-0.75em}
# DATA SKILLS

```{r fig-two-together,  message=FALSE, echo=FALSE, fig.align="center"}
library(wordcloud)
comp_skills <- read.csv("data/computing_skills.csv")
pal <- brewer.pal(8, "Dark2")
# pal <- pal[-(1)]
set.seed(99)
# wp_cols <- c("#9d0079","#92c4ff",  "#ff64b9",  "#5677ff",  "#7c8900",  "#02b1f9",  "#fdb78b",  "#59488a")
wordcloud(comp_skills$word, comp_skills$freq, scale = c(4, .5), min.freq = 2, max.words = Inf, random.order = TRUE, random.color = TRUE, rot.per = 0, colors = wp_cols)
```


# VALUE ADD
```{r, echo = FALSE, warning=FALSE, fig.height=1.3}
# Create dataframe
wendys_value <- data.frame(cat = c("Apple now", "Apple with Wendy"), vals = c(10, 11))

# Factor categories to control plotting order
wendys_value$cat <- factor(wendys_value$cat, levels = c("Apple with Wendy", "Apple now"))

ggplot(wendys_value, aes(x = vals, y = cat, group = cat)) +
  geom_bar(stat = "identity", width = 0.75, aes(fill = cat)) +
  theme_classic(base_size = 16) +
  scale_x_continuous(limits = c(0, 11), breaks = c(0, 5, 10), expand = c(0, 0)) +
  labs(y = "", x = "Score") +
  theme(
    legend.position = "none",
    axis.text.y = element_text(
      color = "#3591aa",
      size = 14,
      face = "bold"
    ),
    axis.ticks.y = element_blank()
  ) +
  scale_fill_manual(values = c("#D4AF37", "#C0C0C0"))
```

:::
::::::
