---
title: "Résumé"
author: "Wendy Phillips"
date: "8/12/2023"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    dev: cairo_pdf
    template: svm-latex-resume.tex
fontawesome: FALSE
linestretch: TRUE
colorlinks: TRUE

geometry: "top=.75in, left =.75in, right=.75in, bottom=.75in"
mainfont: Proxima Nova
sansfont: Proxima Nova
monofont: Proxima Nova 
urlcolor: CadetBlue
fontsize: 11pt
summary: "Curiosity driven to uncover the hidden gems in data. Passionate about communicating findings to others in audience-appropriate manner."

includephoto: FALSE
---

```{r setup, include=FALSE, echo=FALSE}
library(ggplot2)
```

<!-- Read more about Pandoc's [fenced_divs](https://pandoc.org/MANUAL.html#extension-fenced_divs) syntax -->

:::::: {.columns}
::: {.column width="57%" data-latex="{0.57\textwidth}"}

# EXPERIENCE

## \textcolor{MidnightBlue}{Senior Bioinformatician}
\vspace{-0.75em}
2020 - present, Diversigen, New Brighton, MN  

- Author R package of data manipulation, visualization, and statisical functions routinely used by team members
- Maintain R package on github, incorporating team member suggestions
- Produce over 20 written reports containing statistical analyses and data visualization

## \textcolor{MidnightBlue}{Research Scientist}
\vspace{-0.75em}
2018 - 2020, Elanco, Greenfield, IN 

- Perform statistical analyses and create data visualizations
- Present findings to internal teams, customizing for audience backgrounds
- Taught team members basic analytic and visualization methods


## \textcolor{MidnightBlue}{Business Owner}
\vspace{-0.75em}
2016 - 2018, Wendy Phillips Photography, Corvallis, OR

- Founded and managed self-owned photography business


## \textcolor{MidnightBlue}{Research Associate}
\vspace{-0.75em}
2013 - 2016, U.S. Dept. of Agriculture,  Corvallis, OR  

- Statistical analysis
- Another
- Another

## **ACTIVITY OVER TIME**
```{r, echo=FALSE, message = FALSE}
library(tidyverse)
library(RColorBrewer)
act <- read.csv("/Users/wendyphillips/Documents/Computing/R_work/data/Activities.csv", check.names = FALSE)
act <- act[,1:8]
act_long <- act |> pivot_longer(cols = 2:8)
act_long <- act_long |> rename(Activity = name)
act_long$Activity <- factor(act_long$Activity, level = c("Data_analysis", "Research", "Writing" ,"Presenting", "Learning", "Teaching", "Other"))
pal <- brewer.pal(8,"Dark2")

ggplot(act_long, aes(x = Year, y = value, fill = Activity)) +
  geom_area(stat= 'identity', position = "stack") +
  theme_classic(base_size = 14) +
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand = c(0,0), breaks = c(2000,2005,2010,2015,2020)) +
  labs(y = "Percent of working time") +
  theme(legend.position = "top") +
  scale_fill_brewer(type = "qual",palette =  "Dark2")

```


:::
::: {.column width="5%" data-latex="{0.05\textwidth}"}
\ 
<!-- an empty div with an empty character to serve as a column sep -->
:::
:::::: {.column width="38%" data-latex="{0.38\textwidth}"}

# CONTACT INFORMATION

wendyphillips@gmail.com  
541-230-8048  
Golden Valley, MN

# WEB LINKS
[LinkedIn](https://https://www.linkedin.com/in/wendyphillipsphd/)  
[GitHub](https://github.com/wendysphillips)  

# SKILLS
```{r fig-two-together,  message=FALSE, echo=FALSE}
library(wordcloud) 
comp_skills <- read.csv("/Users/wendyphillips/Documents/Computing/R_work/data/computing_skills.csv")
pal <- brewer.pal(6,"Dark2")
pal <- pal[-(1)]
set.seed(997)
wordcloud(comp_skills$word, comp_skills$freq, scale=c(4,.5),min.freq=2,max.words=Inf,
          random.order=TRUE, random.color=TRUE, rot.per=.15, fixed.asp = TRUE,
          colors=pal)
```

```{r,  message=FALSE, echo=FALSE}
library(treemap) 
skills <- read.csv("skills.csv")
treemap(skills, index=c("Group","Subgroup"), vSize="value", type="index",
        fontsize.labels=c(10,8),                # size of labels. Give the size per level of aggregation: size for group, size for subgroup, sub-subgroups...
        fontcolor.labels=c("white","orange"),    # Color of labels
        fontface.labels=c(2,1),                  # Font of labels: 1,2,3,4 for normal, bold, italic, bold-italic...
        bg.labels=c("transparent"),              # Background color of labels
        align.labels=list(
          c("center", "center"), 
          c("center", "center")
        ),                                   # Where to place labels in the rectangle?
        overlap.labels=1,                      # number between 0 and 1 that determines the tolerance of the overlap between labels. 0 means that labels of lower levels are not printed if higher level labels overlap, 1  means that labels are always printed. In-between values, for instance the default value .5, means that lower level labels are printed if other labels do not overlap with more than .5  times their area size.
        inflate.labels=T,                        # If true, labels are bigger when rectangle is bigger.
        aspRatio = 1.5,
        lowerbound.cex.labels=0,
        palette="-RdGy"
)
```



# EDUCATION
Ph.D. Environmental Sciences  
Oregon State University  
\    
B.A. Biological Sciences  
The University of Chicago  
 



:::
::::::

