---
title: "Résumé"
author: "Wendy Phillips"
date: "8/12/2023"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    dev: cairo_pdf
    template: svm-latex-resume.tex
fontawesome: FALSE
linestretch: TRUE
colorlinks: TRUE

geometry: "top=.75in, left =.75in, right=.75in, bottom=.75in"
mainfont: Proxima Nova
sansfont: Proxima Nova
monofont: Proxima Nova 
urlcolor: CadetBlue
fontsize: 11pt
summary: "Driven by curiosity to uncover the hidden gems in data, with out of the box thinking that solves problems. My insight into others' needs drives my clear, impactful communication of results."  

includephoto: FALSE
---

```{r setup, include=FALSE, echo=FALSE}
library(tidyverse)
library(RColorBrewer)
```

:::::: {.columns}
::: {.column width="57%" data-latex="{0.57\textwidth}"}

# EXPERIENCE
\vspace{0em}
## **WORK ACTIVITY HISTORY**
```{r, echo=FALSE, message = FALSE}
# Read in and subset data
act <- read.csv("data/Activities.csv", check.names = FALSE)
act <- act[, 1:8]

# Transform to long format for plotting
act_long <- act |> pivot_longer(cols = 2:8)
act_long <- act_long |> rename(Activity = name)

# Change underscore to space
act_long$Activity <- gsub("Analyze_data", "Analyze data", act_long$Activity)

# Factor activities by desired plotting order
act_long$Activity <- factor(act_long$Activity, level = c("Analyze data", "Research", "Write", "Present", "Learn", "Teach", "Create"))

# pal <- c(brewer.pal(6,"Dark2"), "#573db3")

ggplot(act_long, aes(x = Year, y = value, fill = Activity)) +
  geom_area(stat = "identity", position = "stack") +
  theme_classic(base_size = 14) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0), breaks = c(2000, 2005, 2010, 2015, 2020)) +
  labs(y = "Percent of working time") +
  theme(legend.position = "top") +
  scale_fill_brewer(type = "qual", palette = "Dark2")
```


## \textcolor{BlueViolet}{Senior Bioinformatician}
\vspace{-0.75em}
2020 - present, *Diversigen*, New Brighton, MN  

\small
\vspace{-0.65em}
- Collaborate with internal and external teams to understand goals, execute data analysis, return figures & statistical results
- Create R package of visualization and statistical functions used by team members, incorporate feedback, maintain on github
- Produce over 20 written reports containing statistical analyses & data visualization
- Spearhead analysis of multi-faceted internal research project, present findings at national conference

\vspace{-1.5em}
## \textcolor{BlueViolet}{Research Scientist}
\vspace{-0.75em}
2018 - 2020, *Elanco*, Greenfield, IN 

\vspace{-0.65em}
- Performed quality control, exploratory & statistical analysis on research data, produced summary visualizations, wrote reports
- Presented findings to internal teams & at external conferences, customizing information for audience backgrounds
- Taught team members basic analytic and visualization methods

\vspace{-1.5em}
## \textcolor{BlueViolet}{Business Owner}
\vspace{-0.75em}
2016 - 2018, *Wendy Phillips Photography*, Corvallis, OR

\vspace{-0.65em}
- Founded and managed self-owned photography business

\vspace{-1.5em}
## \textcolor{BlueViolet}{Research Associate}
\vspace{-0.75em}
2013 - 2016, *U.S. Dept. of Agriculture*,  Corvallis, OR  

\vspace{-0.65em}
- Managed five concurrent research projects, performed both research and data analytics, yielding five scientific publications

:::
::: {.column width="5%" data-latex="{0.05\textwidth}"}
\ 
<!-- an empty div with an empty character to serve as a column sep -->
:::
:::::: {.column width="38%" data-latex="{0.38\textwidth}"}

# CONTACT INFORMATION
\vspace{-0.5em}
wendyphillips@gmail.com  
541-230-8048  
Golden Valley, MN  

\vspace{-0.75em}
# LINKS
\vspace{-0.5em}
[GitHub](https://github.com/wendysphillips)  
[LinkedIn](https://https://www.linkedin.com/in/wendyphillipsphd/)  

\vspace{-0.75em}
# EDUCATION
\vspace{-0.5em}
**Ph.D.** Environmental Sciences  
Oregon State University, 2012   

**B.A.** Biological Sciences  
The University of Chicago, 1992 

\vspace{-0.75em}
# CERTIFICATIONS
\vspace{-0.5em}
[Professional Data Scientist](https://www.datacamp.com/certificate/DS0027755206453)      
DataCamp, 2023

\vspace{-0.75em}
# DATA SKILLS

```{r fig-two-together,  message=FALSE, echo=FALSE, fig.align="center"}
library(wordcloud)
comp_skills <- read.csv("data/computing_skills.csv")
pal <- brewer.pal(8, "Dark2")
# pal <- pal[-(1)]
set.seed(997)
# wp_cols <- c("#9d0079","#92c4ff",  "#ff64b9",  "#5677ff",  "#7c8900",  "#02b1f9",  "#fdb78b",  "#59488a")
wordcloud(comp_skills$word, comp_skills$freq, scale = c(4, .5), min.freq = 2, max.words = Inf, random.order = TRUE, random.color = TRUE, rot.per = 0, colors = pal)
```


# VALUE ADD
```{r, echo = FALSE, warning=FALSE, fig.height=1.3}
# Create dataframe
wendys_value <- data.frame(cat = c("apple now", "apple with wendy"), vals = c(10, 11))

# Factor categories to control plotting order
wendys_value$cat <- factor(wendys_value$cat, levels = c("apple with wendy", "apple now"))

ggplot(wendys_value, aes(x = vals, y = cat, group = cat)) +
  geom_bar(stat = "identity", width = 0.75, aes(fill = cat)) +
  theme_classic(base_size = 16) +
  scale_x_continuous(limits = c(0, 11), breaks = c(0, 5, 10), expand = c(0, 0)) +
  labs(y = "", x = "Score") +
  theme(
    legend.position = "none",
    axis.text.y = element_text(
      color = "#3591aa",
      size = 14,
      face = "bold"
    ),
    axis.ticks.y = element_blank()
  ) +
  scale_fill_manual(values = c("#D4AF37", "#C0C0C0"))
```

:::
::::::
