---
title: "Résumé"
author: "Wendy Phillips"
date: "8/12/2023"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    dev: cairo_pdf
    template: svm-latex-resume.tex
fontawesome: FALSE
linestretch: TRUE
colorlinks: TRUE

geometry: "top=.75in, left =.75in, right=.75in, bottom=.75in"
mainfont: Proxima Nova
sansfont: Proxima Nova
monofont: Proxima Nova 
urlcolor: CadetBlue
fontsize: 11pt
summary: "Driven by intense curiosity to uncover the hidden gems in data. Highly experienced in data analytics. Passionate about communicating results in an audience-appropriate manner."  

includephoto: FALSE
---

```{r setup, include=FALSE, echo=FALSE}
library(ggplot2)
```

<!-- Read more about Pandoc's [fenced_divs](https://pandoc.org/MANUAL.html#extension-fenced_divs) syntax -->

:::::: {.columns}
::: {.column width="57%" data-latex="{0.57\textwidth}"}

# EXPERIENCE
\vspace{0em}
## **WORK ACTIVITY HISTORY**
```{r, echo=FALSE, message = FALSE}
library(tidyverse)
library(RColorBrewer)
act <- read.csv("/Users/wendyphillips/Documents/Computing/R_work/data/Activities.csv", check.names = FALSE)
act <- act[,1:8]
act_long <- act |> pivot_longer(cols = 2:8)
act_long <- act_long |> rename(Activity = name)
act_long$Activity <- factor(act_long$Activity, level = c("Data_analysis", "Research", "Writing" ,"Presenting", "Learning", "Teaching", "Other"))
pal <- brewer.pal(8,"Dark2")

ggplot(act_long, aes(x = Year, y = value, fill = Activity)) +
  geom_area(stat= 'identity', position = "stack") +
  theme_classic(base_size = 14) +
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand = c(0,0), breaks = c(2000,2005,2010,2015,2020)) +
  labs(y = "Percent of working time") +
  theme(legend.position = "top") +
  scale_fill_brewer(type = "qual",palette =  "Dark2")

```


## \textcolor{MidnightBlue}{Senior Bioinformatician}
\vspace{-0.75em}
*2020 - present*, Diversigen, New Brighton, MN  

- Author R package of data manipulation, visualization, and statisical functions routinely used by team members
- Maintain R package on github, incorporating team member suggestions
- Produce over 20 written reports containing statistical analyses and data visualization

\vspace{-1.em}
## \textcolor{MidnightBlue}{Research Scientist}
\vspace{-0.75em}
*2018 - 2020*, Elanco, Greenfield, IN 

- Perform statistical analyses and create data visualizations
- Present findings to internal teams, customizing for audience backgrounds
- Taught team members basic analytic and visualization methods

\vspace{-1.em}
## \textcolor{MidnightBlue}{Business Owner}
\vspace{-0.75em}
*2016 - 2018*, Wendy Phillips Photography, Corvallis, OR

- Founded and managed self-owned photography business

\vspace{-1.em}
## \textcolor{MidnightBlue}{Research Associate}
\vspace{-0.75em}
*2013 - 2016*, U.S. Dept. of Agriculture,  Corvallis, OR  

- Statistical analysis
- Another

:::
::: {.column width="5%" data-latex="{0.05\textwidth}"}
\ 
<!-- an empty div with an empty character to serve as a column sep -->
:::
:::::: {.column width="38%" data-latex="{0.38\textwidth}"}

# CONTACT INFORMATION
\vspace{-0.5em}
wendyphillips@gmail.com  
541-230-8048  
Golden Valley, MN  

\vspace{-0.75em}
# LINKS
\vspace{-0.5em}
[LinkedIn](https://https://www.linkedin.com/in/wendyphillipsphd/)  
[GitHub](https://github.com/wendysphillips)  

\vspace{-0.75em}
# EDUCATION
\vspace{-0.5em}
**Ph.D.** Environmental Sciences  
Oregon State University, 2012   

**B.A.** Biological Sciences  
The University of Chicago, 1992 

\vspace{-0.75em}
# CERTIFICATIONS
\vspace{-0.5em}
[Professional Data Scientist](https://www.datacamp.com/certificate/DS0027755206453)      
DataCamp, 2023

\vspace{-0.75em}
# DATA SKILLS

```{r fig-two-together,  message=FALSE, echo=FALSE, fig.align="center"}
library(wordcloud) 
comp_skills <- read.csv("/Users/wendyphillips/Documents/Computing/R_work/data/computing_skills.csv")
pal <- rev(brewer.pal(8,"Dark2"))
# pal <- pal[-(1)]
set.seed(9999)
wordcloud(comp_skills$word, comp_skills$freq, scale=c(4,.5),min.freq=2,max.words=Inf,random.order=TRUE, random.color=TRUE, rot.per=0, colors=pal)
```


# VALUE ADD
```{r, echo = FALSE, warning=FALSE, fig.height=1.3}

wendys_value <- data.frame(cat = c("apple now", "apple with wendy"), vals = c(10,11))
wendys_value$cat <- factor(wendys_value$cat, levels =c("apple with wendy", "apple now"))
ggplot(wendys_value, aes(x=vals, y = cat, group = cat)) +
  geom_bar(stat='identity', width=0.75,aes(fill = cat)) +
  theme_classic(base_size = 16) +
  scale_x_continuous(limits = c(0,11), breaks = c(0,5,10), expand = c(0,0)) +
  labs(y="", x = "Score") +
  theme(legend.position = "none",
        axis.text.y = element_text(color = "#3591aa", size = 14, face = "bold")) +
  scale_fill_manual(values = c( "#D4AF37", "#C0C0C0")) +
  theme(axis.ticks.y = element_blank())
  
```

 



:::
::::::

